---
title: "Course9_Assignment_Shiny"
author: "Silvia Benitez"
date: "12/5/2017"
output: html_document
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This R Markdown document is made interactive using Shiny.

Please read the instructions to get started with the application.

Once you have read the instructions please go to the following link to see the app in shiny server: 10.0.0.18:3838/ShinyApp_Assignment1/  


## Monitoring Operating Time of CNC machine

This shiny app show data from april 17th to 23th, 2017. You can select a date between that range and you will see some data plotted.

You can also select the range of hours to select which data you want to see of the day. By default will also show two shifts from 7 to 15 and 15 to 23.

The data was gotten from CNC machine of 4 plants: MTY (Monterrey), GDL (Guadalajara), QTO (Queretaro) and SALT (Saltillo). 
Each plant has different machines; for example if you select MTY then you can select within 7 different CNC Machines, if you select GDL then you can select within 2 CNC machines and so on, this because all plants has different CNC machines.

There are 4 tabsets, the first one display a graph which plot day`s hour against the total operating time that the machine was operating within each hour. For example on day april 21st, 2017 at 3 pm (hour = 15) the machine W11 from plant MTY it was not used at all.

The second tabset, print two tables that show summary by machine and summary by plant comparing the operating time of each machine by the total shift hours (Tot_Hrs_Op/Tot_Hrs_Turnos) in porcentage between the date range that is selected by the user.

The third and fourth tabsets, shows the data sets used for tabset 1 and 2.

```{r, echo=FALSE, comment=NA, warning=FALSE,message=FALSE}
library(RMySQL)
library(ggplot2)
library(plyr)
library(plotly)
library(dplyr)
library(data.table)

titlePanel("Production Control 3G")
        sidebarLayout(
                
                sidebarPanel(
                        conditionalPanel(
                                'input.dataset === "Display Graph"',
                        
                        dateInput("date", label = ("Select a Date:"), value = "2017-04-21"),
                        sliderInput("sliderTurnos","Select hours:",
                                    0,23, value = c(7,23)), ##input that will be taken
                        radioButtons("plant", label = ("Select a Plant:"), 
                                    choices = c("MTY" = "MTY", "GDL" = "GDL", "QTO" = "QTO", 
                                                   "SALT" = "SALT"),
                                    selected = "MTY"),
                        
                        conditionalPanel(
                        condition = "input.plant == 'GDL'",
                        selectInput("G", label = ("Select a Machine from GDL:"), 
                                    choices = c("W01" = "W01", "W02" = "W02"),
                                    selected = "W01", multiple = FALSE)),
                        
                        conditionalPanel(
                                condition = "input.plant == 'MTY'",
                                selectInput("M", label = ("Select a Machine from MTY:"), 
                                            choices = c("W03" = "W03", "W06" = "W06", "W07" = "W07",
                                                        "W08" = "W08", "W09" = "W09", "W10" = "W10", 
                                                        "W11" = "W11"),
                                            selected = "W11", multiple = FALSE)),
                        
                        conditionalPanel(
                        condition = "input.plant == 'QTO'",
                        selectInput("Q", label = ("Select a Machine from QTO:"), 
                                    choices = c("W04" = "W04"),
                                    selected = "W04", multiple = FALSE)),
                        
                        conditionalPanel(
                        condition = "input.plant == 'SALT'",
                        selectInput("S", label = ("Select a Machine from SALT:"), 
                                    choices = c("W11" = "W11"),
                                    selected = "W11", multiple = FALSE))
                ),
                
                conditionalPanel(
                        'input.dataset === "Summary"',
                        dateRangeInput("date2", label = ("Select a Date:"), 
                                       start = "2017-04-17",
                                       end = "2017-04-23",
                                       format = "yyyy-mm-dd",
                                       weekstart = 1)
                        ##sliderInput("sliderTurnos2","Select hours:",
                        ##            0,23, value = c(7,15)) ##input that will be taken
                        
                ),
                
                
                conditionalPanel(
                        'input.dataset === "Data OpTime"',
                        dateRangeInput("date4", label = ("Select a Date:"),
                                       start = "2017-04-17",
                                       end = "2017-04-23", 
                                       format = "yyyy-mm-dd",
                                       weekstart = 1)
                ),
                
                conditionalPanel(
                        'input.dataset === "Data Turnos"',
                        dateRangeInput("date5", label = ("Select a Date:"),
                                       start = "2017-04-17",
                                       end = "2017-04-23", 
                                       format = "yyyy-mm-dd",
                                       weekstart = 1)
                )
                
                ),
                mainPanel(
                        tabsetPanel(
                                id = 'dataset',
                        tabPanel("Display Graph", plotlyOutput("plot")),
                        tabPanel("Summary",h4("Summary by Machine"),tableOutput("summary"),
                                 h4("Summary by Plant"), tableOutput("summaryplanta")),
                        tabPanel("Data OpTime", tableOutput("data")),
                        tabPanel("Data Turnos", tableOutput("dataturnos"))
                        )
                        
                   
                        
                )
                
        )
        
        diasetdb <- dbConnect(MySQL(), user = "diaset", password = "diaset00", host = "201.134.41.123", 
                      port = 3337, dbname = "diaset_dwh00")

tb_agg <- dbGetQuery(diasetdb,"SELECT * FROM fact_optime_agg2")
tb_turnos <- dbGetQuery(diasetdb,"SELECT * FROM fact_turnos_3g") 

        ##Update the machine that correspond to each plant
        machine <- reactive({switch(
                input$plant,
                "MTY" = input$M,
                "GDL" = input$G,
                "QTO" = input$Q,
                "SALT" = input$S
                
        )})
        
        output$plot <- renderPlotly({
                
                Var_idDate<-input$date
                t1 <- input$sliderTurnos[1]
                t2 <- input$sliderTurnos[2]
                tb_agg_0sub <- subset(tb_agg,tb_agg$plant==as.character(input$plant))
                nrow(tb_agg_0sub)
                tb_agg_sub <- subset(tb_agg_0sub,tb_agg_0sub$idmachine==machine())
                nrow(tb_agg_sub)
                ##tb_agg_sub$fecha<-as.Date(tb_agg_sub$fecha)
                tb_agg_sub2<- tb_agg_sub[tb_agg_sub$fecha==as.Date(Var_idDate),]
                nrow(tb_agg_sub2)
                Hour <- tb_agg_sub2[,5]
                OpTimePerHour <- (tb_agg_sub2[,6]/3600)
                p <- ggplot(tb_agg_sub2, aes(x = Hour,y = OpTimePerHour))
                p +geom_bar(stat = "identity", fill="#009E73", colour = "black") + 
                        ggtitle("Machine Operating Time per Hour") + 
                        xlab("Hour") + ylab ("optime") + theme_classic(base_size = 14) +
                        scale_x_continuous(breaks=c(t1:t2), labels=c(t1:t2),limits=c(t1-1,t2))
                
        })
        
        ##Table that shows a summary by plant and idmachine
        output$summary <- renderTable({
                tb_agg$plant <- as.factor(tb_agg$plant)
                tb_turnos$plant <- as.factor(tb_turnos$plant)
                tb_agg$idmachine <- as.factor(tb_agg$idmachine)
                tb_turnos$idmachine <- as.factor(tb_turnos$idmachine)
                tb_agg$fecha <- as.Date(tb_agg$fecha)
                tb_turnos$fecha <- as.Date(tb_turnos$fecha)
                df <- select(tb_agg,plant:sum_machine_optime)
                
                tb_turnos_ord <- tb_turnos[,c(1,2,3,4,9,5,6,7,8)]
                df_turnos <- select(tb_turnos_ord,plant:total_hrs)
                
                idDate<-as.Date(input$date2[2])
                idDate2 <- as.Date(input$date2[1])
                
                ##new table with specific date
                df <- df[(df$fecha >= as.Date(idDate2) & df$fecha <= as.Date(idDate)),] 
                df_turnos <- df_turnos[(df_turnos$fecha >= as.Date(idDate2) & 
                                                df_turnos$fecha <= as.Date(idDate)),] 
                ##add another column to put optime in hrs round to 2 digits
                df1 <- mutate(df, optime_hr = round((sum_machine_optime/3600),2))
               
                ##Group table by plant, idmachine,fecha and summarize optime_hr
                df_3g <- df1 %>% group_by(plant,idmachine,fecha) %>% 
                        summarise (Tot_Hrs_Op = sum(optime_hr))
                
                ##Merge the column Tot_Hrs_Op from table df_3g to table df_turnos
                df_turnos <- data.table(df_turnos)
                df_3g <- data.table(df_3g)
                setkey(df_turnos,plant,idmachine,fecha)
                setkey(df_3g,plant,idmachine,fecha)
                df_3g_turnos <- merge(df_turnos, df_3g, all = TRUE)
                
                ##Group data by plant, idmachine and show table according date input in app
                df_3G <- df_3g_turnos %>% group_by(plant,idmachine) %>% 
                        summarise(Tot_Hrs_Turnos = sum(total_hrs,na.rm=TRUE), 
                                        Tot_Hrs_Op = round((sum(Tot_Hrs_Op,na.rm=TRUE)),2))
                
                ##Table with Total de Horas operando y Porcentaje de las horas operando por planta y maquina
                df_3G_1 <- mutate(df_3G, Porc_Op = round(((Tot_Hrs_Op/Tot_Hrs_Turnos)*100),2))
                
                df_3G_1
                
                
                })
        
        ##Table that shows a summary by plant
        output$summaryplanta <- renderTable({
                tb_agg$plant <- as.factor(tb_agg$plant)
                tb_turnos$plant <- as.factor(tb_turnos$plant)
                tb_agg$idmachine <- as.factor(tb_agg$idmachine)
                tb_turnos$idmachine <- as.factor(tb_turnos$idmachine)
                tb_agg$fecha <- as.Date(tb_agg$fecha)
                tb_turnos$fecha <- as.Date(tb_turnos$fecha)
                df <- select(tb_agg,plant:sum_machine_optime)
                
                tb_turnos_ord <- tb_turnos[,c(1,2,3,4,9,5,6,7,8)]
                df_turnos <- select(tb_turnos_ord,plant:total_hrs)
                
                idDate<-as.Date(input$date2[2])
                idDate2 <- as.Date(input$date2[1])
                ##idDate <- as.Date("2017-04-23")
                ##idDate2 <- as.Date("2017-04-17")
                
                ##new table with specific date
                df <- df[(df$fecha >= as.Date(idDate2) & df$fecha <= as.Date(idDate)),] 
                df_turnos <- df_turnos[(df_turnos$fecha >= as.Date(idDate2) & 
                                                df_turnos$fecha <= as.Date(idDate)),] 
                ##add another column to put optime in hrs round to 2 digits
                df1 <- mutate(df, optime_hr = round((sum_machine_optime/3600),2))
                
                ##Group table by plant, idmachine,fecha and summarize optime_hr
                df_3g <- df1 %>% group_by(plant,idmachine,fecha) %>% 
                        summarise (Tot_Hrs_Op = sum(optime_hr))
                
                ##Merge the column Tot_Hrs_Op from table df_3g to table df_turnos
                df_turnos <- data.table(df_turnos)
                df_3g <- data.table(df_3g)
                setkey(df_turnos,plant,idmachine,fecha)
                setkey(df_3g,plant,idmachine,fecha)
                df_3g_turnos <- merge(df_turnos, df_3g, all = TRUE)
                
                ##Group data by plant, idmachine and show table according date input in app
                df_3G <- df_3g_turnos %>% group_by(plant,idmachine) %>% 
                        summarise(Tot_Hrs_Turnos = sum(total_hrs,na.rm=TRUE), 
                                  Tot_Hrs_Op = round((sum(Tot_Hrs_Op,na.rm=TRUE)),2))
                
                ##Table with Total de Horas operando y Porcentaje de las horas operando por planta y maquina
                df_3G_1 <- mutate(df_3G, Porc_Op = round(((Tot_Hrs_Op/Tot_Hrs_Turnos)*100),2))
                
                ##Table with Total de Horas operando y Porcentaje de las horas operando por planta
                
                df_3G_Tot <- df_3G_1 %>% group_by(plant) %>% summarise(Tot_Hrs_Op_plant = sum(Tot_Hrs_Op,na.rm=TRUE), 
                                                Porc_Op_plant = round((mean(Porc_Op,na.rm=TRUE)),2))
                
                df_3G_Tot 
                
        })
        
        output$data <- renderTable({
           
                df <- select(tb_agg, plant:sum_machine_optime)
                idDate<-as.Date(input$date4[2])
                idDate2 <- as.Date(input$date4[1])
                ##new table with specific date
                df<- df[(df$fecha >= as.Date(idDate2) & df$fecha <= as.Date(idDate)),] 
                df1 <- mutate(df, optime_hr = sum_machine_optime/3600)
                df2 <- df1[,c(1,2,3,4,6,5)]
                df3 <- select(df2,plant:optime_hr)
                df4 <- arrange(df3, plant, idmachine,fecha,hour)
                df4
        })
        
        output$dataturnos <- renderTable({
                
                tb_turnos_ord <- tb_turnos[,c(1,2,3,4,9,5,6,7,8)]
                df_turnos <- select(tb_turnos_ord,plant:total_hrs)
                idDate<-as.Date(input$date5[2])
                idDate2 <- as.Date(input$date5[1])
                ##new table with specific date
                df_turnos1<- df_turnos[(df_turnos$fecha >= as.Date(idDate2) & 
                                             df_turnos$fecha <= as.Date(idDate)),] 
                df_turnos2 <- arrange(df_turnos1,plant,idmachine,fecha)
                df_turnos2
        })

```





